---
title: "Cost_change_source_cluster_documentation"
author: "Fred Cudhea"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

<style>
pre {
  overflow-x: auto;
}
pre code {
  word-wrap: normal;
  white-space: pre;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

Documentation for R script: Cost_change_source_cluster.r which is called by "LASTING_cluster_w_masterinput.r" and is used to calculate  cost, environment and social pillar impact for a given dietary type and food source (food at home vs food away from home). It will calculate population level and per capita results, and output the full sims, as well as summary stats, into separate output files.

Don't be confused by the name of the file or some of the object names within this script. This is adapted from code that was originally for calculating cost change only, hence the "econ" specific naming conventions peppered throughout.

First, read in functions used to calculate impacts.
```{r read_in_funcs,eval=FALSE,echo=TRUE}
#Cost_change_source.r
#setwd("C:\\Users\\fcudhe01\\Box Sync\\new life\\LASTING\\Code")
setwd("/cluster/tufts/lasting/shared/LASTING/Code")
source("cost_change_functions.r")
```

Define working directory and output location.
```{r pathways,eval=FALSE,echo=TRUE}
#file_location = "C:\\Users\\fcudhe01\\Box\\lasting_aim_3\\data\\in\\example_cra"
#file location already set in "LASTING.r"
setwd(file_location)

output_location = paste("/cluster/tufts/lasting/shared/model_development/data/outputs/cost_env/",
                        costs_output_loc.vec[k], sep="")
```

Read in relevant inputs (population draws, costs and impact factors of dietary factors) and do some minor data processing. Remember, the "impact factors" for cost is the cost for that dietary factor. We are not speculating how much costs for each dietary factor change as intake changes, just how much total spend on food would change (assuming costs stay the same). 
```{r read_in_inputs, eval=FALSE,echo=TRUE}
#pop.sims<-read.csv("population.sims.csv", fileEncoding = 'UTF-8-BOM')
pop.sims<-read.csv("observed.pop.draws.csv", fileEncoding = 'UTF-8-BOM')
#pop.sims$subgroup_id<-pop.sims$subgroup

cost.inputs<-costs_inputs.vec[[k]]
merged<-merge(cost.inputs, pop.sims, by="subgroup_id")
merged$Sex<-merged$Sex.y
merged$population <- merged$population.y
```

Create list objects to store outputs. Each element of the lists corresponds to a specific subgroup. There are 31 lists in total, corresponding so some combination of 1. what we are looking at (impact (as in, change in impact), substitution impact, combined impact (change in impact + substitution impact), population, delta (aka, change in intake), current intake impact, counterfactual intake impact)*, and 2. level of disaggregation (total, consumed, unconsumed, inedible, wasted). Hopefully, what each list corresponds to is clear from name.

* see "cost_change_function_documentation" for more detail on what these things mean
```{r output_lists, echo=TRUE}
################
list.of.impact.sims.total<-list()
list.of.substitution.impact.sims.total<-list()
list.of.combined.impact.sims.total<-list()
list.of.population.sims<-list()
list.of.delta.sims.total<-list()

list.of.impact.sims.consumed<-list()
list.of.substitution.impact.sims.consumed<-list()
list.of.combined.impact.sims.consumed<-list()
list.of.delta.sims.consumed<-list()

list.of.impact.sims.unconsumed<-list()
list.of.substitution.impact.sims.unconsumed<-list()
list.of.combined.impact.sims.unconsumed<-list()
list.of.delta.sims.unconsumed<-list()

list.of.current.intake.impact.sims.total<-list()
list.of.CF.intake.impact.sims.total<-list()
list.of.current.intake.impact.sims.consumed<-list()
list.of.CF.intake.impact.sims.consumed<-list()
list.of.current.intake.impact.sims.unconsumed<-list()
list.of.CF.intake.impact.sims.unconsumed<-list()

list.of.impact.sims.inedible<-list()
list.of.substitution.impact.sims.inedible<-list()
list.of.combined.impact.sims.inedible<-list()
list.of.delta.sims.inedible<-list()

list.of.impact.sims.wasted<-list()
list.of.substitution.impact.sims.wasted<-list()
list.of.combined.impact.sims.wasted<-list()
list.of.delta.sims.wasted<-list()

list.of.current.intake.impact.sims.inedible<-list()
list.of.CF.intake.impact.sims.inedible<-list()
list.of.current.intake.impact.sims.wasted<-list()
list.of.CF.intake.impact.sims.wasted<-list()
```

Rename some variables.
```{r rename_vars, eval=FALSE,echo=TRUE}
n.sims<-nsim1
impact.factor.names<-econ.outcomes.vec
```

Start for loop. We are going to be traversing the "merged" file row by row and calculating impacts. Each row should correspond to a subgroup and dietary factor.
```{r start_for_loop, eval=FALSE,echo=TRUE}
for(i in 1:dim(merged)[1]) ##for each row in the input file (corresponding to fcid for a given subgroup)
{
```

Still in loop: Extract label variables and put them into their own data frames (to be merged later with the results).
```{r keep_var_names, eval=FALSE,echo=TRUE}
  print(i)
  vars.to.keep.for.df.a<-c("Foodgroup", "sex_gp", "race_gp", "age_gp",
                           "subgroup_id", "population", 
                           "Mean_Intake", "SE_Intake", "CF_Mean_Intake", "CF_SE_Intake", "Intake_unit", 
                           
                           # "CED_unit", "GHG_unit", "WATER_unit","BLUEWATER_unit", "Food_price_unit", "FL_unit",
                           # "CED_to_intake_conversion",
                           # "GHG_to_intake_conversion",
                           # "WATER_to_intake_conversion",
                           # "BLUEWATER_to_intake_conversion",
                           # "Food_price_to_intake_conversion",
                           # "FL_to_intake_conversion",
                           
                           paste0(all.outcomes.vec, "_unit"),
                           paste0(all.outcomes.vec, "_to_intake_conversion"))
  
  df.a<-merged[i, vars.to.keep.for.df.a] 
```

Still in loop: Here, we are just creating a data frame that repeats df.a for however many outcomes we are looking at (six, in our case). We are going to have results for each pair of dietary factor and outcome.  
```{r df.aa, eval=FALSE,echo=TRUE}  
  df.aa<-df.a[rep(seq_len(nrow(df.a)), each = length(impact.factor.names)),]
```

Still in loop: For the sake of readability of code, we extract various relevant inputs from merged[i,] and give them their own object with own name.
```{r extract_inputs, eval=FALSE,echo=TRUE}
  current.mean<-merged[i,"Mean_Intake"]
  current.se<-merged[i,"SE_Intake"]
  counterfactual.mean<-merged[i,"CF_Mean_Intake"]
  counterfactual.se<-merged[i,"CF_SE_Intake"]
  impact.factor.means<-merged[i,econ.outcomes.vec.mn]
  impact.factor.ses<-merged[i,econ.outcomes.vec.se]
  #RRunit<-merged[i, "price_to_intake_conversion"]
  
  # idk why this isn't working
  # RRunit<-merged[i, c("CED_to_intake_conversion", "GHG_to_intake_conversion", 
  #                     "WATER_to_intake_conversion", "BLUEWATER_to_intake_conversion",
  #                     "Food_price_to_intake_conversion", "FL_to_intake_conversion")]
  
  # new
  RRunit <- merged %>% select(c(paste0(impact.factor.names, "_to_intake_conversion"))) %>% 
    slice(1)
  
  
  pop.sims.names<-paste("X", c(1:n.sims), sep="")
  population.sims<-matrix(rep(x=as.numeric(merged[i, pop.sims.names]), times=length(impact.factor.names)), nrow=length(impact.factor.names))
  #population.sims<-as.numeric(merged[i, pop.sims.names])
  #population<-merged[i, "population"]
  #population.se<-merged[i, "population.se"]
  
  substitution.impact.factor.means<-merged[i,econ.outcomes.substitution.vec.mn]
  substitution.impact.factor.ses<-merged[i,econ.outcomes.substitution.vec.se]
  substitution_unit<-merged[i,"substitution_unit"] 
  
  current_inedible_p<-merged[i,econ.current.inedible.p.mn]
  current_inedible_p_se<-merged[i,econ.current.inedible.p.se]
  current_foodwaste_p<-merged[i,econ.current.foodwaste.p.mn]
  current_foodwaste_p_se<-merged[i,econ.current.foodwaste.p.se]
  counterfactual_inedible_p<-merged[i,econ.counterfactual.inedible.p.mn]
  counterfactual_inedible_p_se<-merged[i,econ.counterfactual.inedible.p.se]
  counterfactual_foodwaste_p<-merged[i,econ.counterfactual.foodwaste.p.mn]
  counterfactual_foodwaste_p_se<-merged[i,econ.counterfactual.foodwaste.p.se]
```

Still in loop: Take the above inputs and feed it into function that simulates the impact (simulate.impact). The resulting "b" is a list of 31 matrices with simulation results that correspond to the 31 lists we made earlier.
```{r simulate_impact, eval=FALSE,echo=TRUE}
  b<-simulate.impact(current.mean=current.mean, current.se=current.se, counterfactual.mean=counterfactual.mean,
                     counterfactual.se=counterfactual.se, impact.factor.names=impact.factor.names, 
                     impact.factor.means=as.numeric(impact.factor.means), impact.factor.ses=as.numeric(impact.factor.ses),
                     RRunit=RRunit, 
                     substitution.impact.factor.means=as.numeric(substitution.impact.factor.means),
                     substitution.impact.factor.ses=as.numeric(substitution.impact.factor.ses), 
                     substitution_unit=substitution_unit, 
                     current_inedible_p=as.numeric(current_inedible_p),
                     current_inedible_p_se=as.numeric(current_inedible_p_se),
                     current_foodwaste_p=as.numeric(current_foodwaste_p),
                     current_foodwaste_p_se=as.numeric(current_foodwaste_p_se),
                     counterfactual_inedible_p=as.numeric(counterfactual_inedible_p),
                     counterfactual_inedible_p_se=as.numeric(counterfactual_inedible_p_se),
                     counterfactual_foodwaste_p=as.numeric(counterfactual_foodwaste_p),
                     counterfactual_foodwaste_p_se=as.numeric(counterfactual_foodwaste_p_se),
                     n.sims=n.sims,
                     population.sims=population.sims)
```

Still in loop: Extract results from "b" (which itself is a list of 31 matrices) # and create data frames with proper labels.
```{r results_as_df_dfb, eval=FALSE,echo=TRUE}
  df.b1<-data.frame(outcome=rownames(b[[1]]), b[[1]])
  df.b2<-data.frame(outcome=rownames(b[[2]]), b[[2]])
  df.b3<-data.frame(outcome=rownames(b[[3]]), b[[3]])
  df.b4<-data.frame(outcome=rownames(b[[4]]), b[[4]])
  df.b5<-data.frame(outcome=rownames(b[[5]]), b[[5]])
  
  df.b6<-data.frame(outcome=rownames(b[[6]]), b[[6]])
  df.b7<-data.frame(outcome=rownames(b[[7]]), b[[7]])
  df.b8<-data.frame(outcome=rownames(b[[8]]), b[[8]])
  df.b9<-data.frame(outcome=rownames(b[[9]]), b[[9]])
  
  df.b10<-data.frame(outcome=rownames(b[[10]]), b[[10]])
  df.b11<-data.frame(outcome=rownames(b[[11]]), b[[11]])
  df.b12<-data.frame(outcome=rownames(b[[12]]), b[[12]])
  df.b13<-data.frame(outcome=rownames(b[[13]]), b[[13]])
  
  df.b14<-data.frame(outcome=rownames(b[[14]]), b[[14]])
  df.b15<-data.frame(outcome=rownames(b[[15]]), b[[15]])
  df.b16<-data.frame(outcome=rownames(b[[16]]), b[[16]])
  df.b17<-data.frame(outcome=rownames(b[[17]]), b[[17]])
  df.b18<-data.frame(outcome=rownames(b[[18]]), b[[18]])
  df.b19<-data.frame(outcome=rownames(b[[19]]), b[[19]])
  
  df.b20<-data.frame(outcome=rownames(b[[20]]), b[[20]])
  df.b21<-data.frame(outcome=rownames(b[[21]]), b[[21]])
  df.b22<-data.frame(outcome=rownames(b[[22]]), b[[22]])
  df.b23<-data.frame(outcome=rownames(b[[23]]), b[[23]])
  
  df.b24<-data.frame(outcome=rownames(b[[24]]), b[[24]])
  df.b25<-data.frame(outcome=rownames(b[[25]]), b[[25]])
  df.b26<-data.frame(outcome=rownames(b[[26]]), b[[26]])
  df.b27<-data.frame(outcome=rownames(b[[27]]), b[[27]])
  
  df.b28<-data.frame(outcome=rownames(b[[28]]), b[[28]])
  df.b29<-data.frame(outcome=rownames(b[[29]]), b[[29]])
  df.b30<-data.frame(outcome=rownames(b[[30]]), b[[30]])
  df.b31<-data.frame(outcome=rownames(b[[31]]), b[[31]])
```  
  
Still in loop: Bind df.aa to the df.bs. So now, the df.cs have the relevant variables for interpreting/labeling results (foodgroup, age/sex/race, etc..., all the variables listed in vars.to.keep.for.df.a)   
```{r results_as_df_dfc, eval=FALSE,echo=TRUE}
  df.c1<-cbind(df.aa, df.b1)
  df.c2<-cbind(df.aa, df.b2)
  df.c3<-cbind(df.aa, df.b3)
  df.c4<-cbind(df.aa, df.b4)
  df.c5<-cbind(df.aa, df.b5)
  
  df.c6<-cbind(df.aa, df.b6)
  df.c7<-cbind(df.aa, df.b7)
  df.c8<-cbind(df.aa, df.b8)
  df.c9<-cbind(df.aa, df.b9)

  df.c10<-cbind(df.aa, df.b10)
  df.c11<-cbind(df.aa, df.b11)
  df.c12<-cbind(df.aa, df.b12)
  df.c13<-cbind(df.aa, df.b13)
  
  df.c14<-cbind(df.aa, df.b14)
  df.c15<-cbind(df.aa, df.b15)
  df.c16<-cbind(df.aa, df.b16)
  df.c17<-cbind(df.aa, df.b17)
  df.c18<-cbind(df.aa, df.b18)
  df.c19<-cbind(df.aa, df.b19)
  
  df.c20<-cbind(df.aa, df.b20)
  df.c21<-cbind(df.aa, df.b21)
  df.c22<-cbind(df.aa, df.b22)
  df.c23<-cbind(df.aa, df.b23)
  
  df.c24<-cbind(df.aa, df.b24)
  df.c25<-cbind(df.aa, df.b25)
  df.c26<-cbind(df.aa, df.b26)
  df.c27<-cbind(df.aa, df.b27)
  
  df.c28<-cbind(df.aa, df.b28)
  df.c29<-cbind(df.aa, df.b29)
  df.c30<-cbind(df.aa, df.b30)
  df.c31<-cbind(df.aa, df.b31)
```  

Still in loop: Create "impact_unit_strings" string vector, which is just the "outcome" variable with "_unit" appended to it. Then, create "outcome_unit" variable for all df.cs. Then, for each df.c, loop through each row and populate "outcome_unit" with the the corresponding unit for that outcome for that row (which is extracted from the row j and column impact_unit_strings[j] for the df.c).    
```{r results_as_df_outcomeunit, eval=FALSE, echo=TRUE}
  impact_unit_strings<-paste(df.b1$outcome, "_unit", sep="")
  
  df.c1$outcome_unit<-NA
  df.c2$outcome_unit<-NA
  df.c3$outcome_unit<-NA
  df.c4$outcome_unit<-NA
  df.c5$outcome_unit<-NA
  
  df.c6$outcome_unit<-NA
  df.c7$outcome_unit<-NA
  df.c8$outcome_unit<-NA
  df.c9$outcome_unit<-NA

  df.c10$outcome_unit<-NA
  df.c11$outcome_unit<-NA
  df.c12$outcome_unit<-NA
  df.c13$outcome_unit<-NA

  df.c14$outcome_unit<-NA
  df.c15$outcome_unit<-NA
  df.c16$outcome_unit<-NA
  df.c17$outcome_unit<-NA
  df.c18$outcome_unit<-NA
  df.c19$outcome_unit<-NA
  
  df.c20$outcome_unit<-NA
  df.c21$outcome_unit<-NA
  df.c22$outcome_unit<-NA
  df.c23$outcome_unit<-NA
  
  df.c24$outcome_unit<-NA
  df.c25$outcome_unit<-NA
  df.c26$outcome_unit<-NA
  df.c27$outcome_unit<-NA
  
  df.c28$outcome_unit<-NA
  df.c29$outcome_unit<-NA
  df.c30$outcome_unit<-NA
  df.c31$outcome_unit<-NA
  
  for(j in 1:dim(df.c1)[1])
  {
    df.c1$outcome_unit[j]<-df.c1[j,impact_unit_strings[j]]
    df.c2$outcome_unit[j]<-df.c2[j,impact_unit_strings[j]]
    df.c3$outcome_unit[j]<-df.c3[j,impact_unit_strings[j]]
    df.c4$outcome_unit[j]<-df.c4[j,impact_unit_strings[j]]
    df.c5$outcome_unit[j]<-df.c5[j,impact_unit_strings[j]]
    
    df.c6$outcome_unit[j]<-df.c6[j,impact_unit_strings[j]]
    df.c7$outcome_unit[j]<-df.c7[j,impact_unit_strings[j]]
    df.c8$outcome_unit[j]<-df.c8[j,impact_unit_strings[j]]
    df.c9$outcome_unit[j]<-df.c9[j,impact_unit_strings[j]]

    df.c10$outcome_unit[j]<-df.c10[j,impact_unit_strings[j]]
    df.c11$outcome_unit[j]<-df.c11[j,impact_unit_strings[j]]
    df.c12$outcome_unit[j]<-df.c12[j,impact_unit_strings[j]]
    df.c13$outcome_unit[j]<-df.c13[j,impact_unit_strings[j]]

    df.c14$outcome_unit[j]<-df.c14[j,impact_unit_strings[j]]
    df.c15$outcome_unit[j]<-df.c15[j,impact_unit_strings[j]]
    df.c16$outcome_unit[j]<-df.c16[j,impact_unit_strings[j]]
    df.c17$outcome_unit[j]<-df.c17[j,impact_unit_strings[j]]
    df.c18$outcome_unit[j]<-df.c18[j,impact_unit_strings[j]]
    df.c19$outcome_unit[j]<-df.c19[j,impact_unit_strings[j]]  
    
    df.c20$outcome_unit[j]<-df.c20[j,impact_unit_strings[j]]
    df.c21$outcome_unit[j]<-df.c21[j,impact_unit_strings[j]]
    df.c22$outcome_unit[j]<-df.c22[j,impact_unit_strings[j]]
    df.c23$outcome_unit[j]<-df.c23[j,impact_unit_strings[j]]
    
    df.c24$outcome_unit[j]<-df.c24[j,impact_unit_strings[j]]
    df.c25$outcome_unit[j]<-df.c25[j,impact_unit_strings[j]]
    df.c26$outcome_unit[j]<-df.c26[j,impact_unit_strings[j]]
    df.c27$outcome_unit[j]<-df.c27[j,impact_unit_strings[j]]
    
    df.c28$outcome_unit[j]<-df.c28[j,impact_unit_strings[j]]
    df.c29$outcome_unit[j]<-df.c29[j,impact_unit_strings[j]]
    df.c30$outcome_unit[j]<-df.c30[j,impact_unit_strings[j]]
    df.c31$outcome_unit[j]<-df.c31[j,impact_unit_strings[j]]
  }
```

Still in loop: move the new "outcome_unit" column to right after "outcome", and get rid of the impact factor specific columns for units.
```{r results_as_df_outcomeunit_relocate, eval=FALSE, echo=TRUE}
  df.c1<- df.c1 %>% relocate(outcome_unit, .after=outcome) %>% select(-impact_unit_strings) ##move the new outcome unit colum to right after outcome, and get rid of the impact factor specfic columns for units
  df.c2<- df.c2 %>% relocate(outcome_unit, .after=outcome) %>% select(-impact_unit_strings)
  df.c3<- df.c3 %>% relocate(outcome_unit, .after=outcome) %>% select(-impact_unit_strings)
  df.c4<- df.c4 %>% relocate(outcome_unit, .after=outcome) %>% select(-impact_unit_strings)
  df.c5<- df.c5 %>% relocate(outcome_unit, .after=outcome) %>% select(-impact_unit_strings)
  
  df.c6<- df.c6 %>% relocate(outcome_unit, .after=outcome) %>% select(-impact_unit_strings)
  df.c7<- df.c7 %>% relocate(outcome_unit, .after=outcome) %>% select(-impact_unit_strings)
  df.c8<- df.c8 %>% relocate(outcome_unit, .after=outcome) %>% select(-impact_unit_strings)
  df.c9<- df.c9 %>% relocate(outcome_unit, .after=outcome) %>% select(-impact_unit_strings)
  
  df.c10<- df.c10 %>% relocate(outcome_unit, .after=outcome) %>% select(-impact_unit_strings)
  df.c11<- df.c11 %>% relocate(outcome_unit, .after=outcome) %>% select(-impact_unit_strings)
  df.c12<- df.c12 %>% relocate(outcome_unit, .after=outcome) %>% select(-impact_unit_strings)
  df.c13<- df.c13 %>% relocate(outcome_unit, .after=outcome) %>% select(-impact_unit_strings)

  df.c14<- df.c14 %>% relocate(outcome_unit, .after=outcome) %>% select(-impact_unit_strings)
  df.c15<- df.c15 %>% relocate(outcome_unit, .after=outcome) %>% select(-impact_unit_strings)
  df.c16<- df.c16 %>% relocate(outcome_unit, .after=outcome) %>% select(-impact_unit_strings)
  df.c17<- df.c17 %>% relocate(outcome_unit, .after=outcome) %>% select(-impact_unit_strings)
  df.c18<- df.c18 %>% relocate(outcome_unit, .after=outcome) %>% select(-impact_unit_strings)
  df.c19<- df.c19 %>% relocate(outcome_unit, .after=outcome) %>% select(-impact_unit_strings)
  
  df.c20<- df.c20 %>% relocate(outcome_unit, .after=outcome) %>% select(-impact_unit_strings)
  df.c21<- df.c21 %>% relocate(outcome_unit, .after=outcome) %>% select(-impact_unit_strings)
  df.c22<- df.c22 %>% relocate(outcome_unit, .after=outcome) %>% select(-impact_unit_strings)
  df.c23<- df.c23 %>% relocate(outcome_unit, .after=outcome) %>% select(-impact_unit_strings)
  
  df.c24<- df.c24 %>% relocate(outcome_unit, .after=outcome) %>% select(-impact_unit_strings)
  df.c25<- df.c25 %>% relocate(outcome_unit, .after=outcome) %>% select(-impact_unit_strings)
  df.c26<- df.c26 %>% relocate(outcome_unit, .after=outcome) %>% select(-impact_unit_strings)
  df.c27<- df.c27 %>% relocate(outcome_unit, .after=outcome) %>% select(-impact_unit_strings)
  
  df.c28<- df.c28 %>% relocate(outcome_unit, .after=outcome) %>% select(-impact_unit_strings)
  df.c29<- df.c29 %>% relocate(outcome_unit, .after=outcome) %>% select(-impact_unit_strings)
  df.c30<- df.c30 %>% relocate(outcome_unit, .after=outcome) %>% select(-impact_unit_strings)
  df.c31<- df.c31 %>% relocate(outcome_unit, .after=outcome) %>% select(-impact_unit_strings)
```

We assign each data frame we made to be the i-th element of their corresponding lists. Recall, earlier in the code, we made 31 different lists to store output (one for each kind of output type). We are now populating that list, the i-th element corresponding to the appropriate df.c. (e.g the current version of df.c1 for this iteration within the for loop is being stored as the i-th element of list.of.impact.sims.total, and so on).
```{r assign_to_lists ,eval=FALSE,echo=TRUE}
  list.of.impact.sims.total[[i]]<-df.c1
  list.of.substitution.impact.sims.total[[i]]<-df.c2
  list.of.combined.impact.sims.total[[i]]<-df.c3
  list.of.population.sims[[i]]<-df.c4
  list.of.delta.sims.total[[i]]<-df.c5
  
  list.of.impact.sims.consumed[[i]]<-df.c6
  list.of.substitution.impact.sims.consumed[[i]]<-df.c7
  list.of.combined.impact.sims.consumed[[i]]<-df.c8
  list.of.delta.sims.consumed[[i]]<-df.c9
  
  list.of.impact.sims.unconsumed[[i]]<-df.c10
  list.of.substitution.impact.sims.unconsumed[[i]]<-df.c11
  list.of.combined.impact.sims.unconsumed[[i]]<-df.c12
  list.of.delta.sims.unconsumed[[i]]<-df.c13
  
  list.of.current.intake.impact.sims.total[[i]]<-df.c14
  list.of.CF.intake.impact.sims.total[[i]]<-df.c15
  list.of.current.intake.impact.sims.consumed[[i]]<-df.c16
  list.of.CF.intake.impact.sims.consumed[[i]]<-df.c17
  list.of.current.intake.impact.sims.unconsumed[[i]]<-df.c18
  list.of.CF.intake.impact.sims.unconsumed[[i]]<-df.c19
  
  list.of.impact.sims.inedible[[i]]<-df.c20
  list.of.substitution.impact.sims.inedible[[i]]<-df.c21
  list.of.combined.impact.sims.inedible[[i]]<-df.c22
  list.of.delta.sims.inedible[[i]]<-df.c23
  
  list.of.impact.sims.wasted[[i]]<-df.c24
  list.of.substitution.impact.sims.wasted[[i]]<-df.c25
  list.of.combined.impact.sims.wasted[[i]]<-df.c26
  list.of.delta.sims.wasted[[i]]<-df.c27
  
  list.of.current.intake.impact.sims.inedible[[i]]<-df.c28
  list.of.CF.intake.impact.sims.inedible[[i]]<-df.c29
  list.of.current.intake.impact.sims.wasted[[i]]<-df.c30
  list.of.CF.intake.impact.sims.wasted[[i]]<-df.c31
```

End the loop.
```{r end_loop, eval=FALSE,echo=TRUE}
}
```

For each list, row-bind the elements of the list (corresponding to a subgroup and dietary factor) together into a data frame. Each of these data frames has results for all dietary factors and subgroups, for one outcome (specified in name of data frame). NAs are also replaced with 0. 

Recall there are 31 lists,each corresponding to some combination of 1. what we are looking at (impact (as in, impact of change), substitution impact, combined impact, population, delta (aka, change in intake), current intake impact, counterfactual intake impact), and 2. level of disaggregation (total, consumed, unconsumed, inedible, wasted).
```{r rbind_the_lists ,eval=FALSE,echo=TRUE}
##not sure why I went with full joint before, rbind is much faster, and shouldn't cause problems.

# added NaN removal on 10/6
impact.sims.total.allgroups<-Reduce(rbind,list.of.impact.sims.total) %>% 
  mutate(across(everything(), ~replace(.x, is.nan(.x), 0)))
substitution.impact.sims.total.allgroups<-Reduce(rbind,list.of.substitution.impact.sims.total) %>% 
  mutate(across(everything(), ~replace(.x, is.nan(.x), 0)))
combined.impact.sims.total.allgroups<-Reduce(rbind,list.of.combined.impact.sims.total) %>% 
  mutate(across(everything(), ~replace(.x, is.nan(.x), 0)))
population.sims.allgroups<-Reduce(rbind,list.of.population.sims) %>% 
  mutate(across(everything(), ~replace(.x, is.nan(.x), 0)))
delta.sims.total.allgroups<-Reduce(rbind,list.of.delta.sims.total) %>% 
  mutate(across(everything(), ~replace(.x, is.nan(.x), 0)))

impact.sims.consumed.allgroups<-Reduce(rbind,list.of.impact.sims.consumed) %>% 
  mutate(across(everything(), ~replace(.x, is.nan(.x), 0)))
substitution.impact.sims.consumed.allgroups<-Reduce(rbind,list.of.substitution.impact.sims.consumed) %>% 
  mutate(across(everything(), ~replace(.x, is.nan(.x), 0)))
combined.impact.sims.consumed.allgroups<-Reduce(rbind,list.of.combined.impact.sims.consumed) %>% 
  mutate(across(everything(), ~replace(.x, is.nan(.x), 0)))
delta.sims.consumed.allgroups<-Reduce(rbind,list.of.delta.sims.consumed) %>% 
  mutate(across(everything(), ~replace(.x, is.nan(.x), 0)))

impact.sims.unconsumed.allgroups<-Reduce(rbind,list.of.impact.sims.unconsumed) %>% 
  mutate(across(everything(), ~replace(.x, is.nan(.x), 0)))
substitution.impact.sims.unconsumed.allgroups<-Reduce(rbind,list.of.substitution.impact.sims.unconsumed) %>% 
  mutate(across(everything(), ~replace(.x, is.nan(.x), 0)))
combined.impact.sims.unconsumed.allgroups<-Reduce(rbind,list.of.combined.impact.sims.unconsumed) %>% 
  mutate(across(everything(), ~replace(.x, is.nan(.x), 0)))
delta.sims.unconsumed.allgroups<-Reduce(rbind,list.of.delta.sims.unconsumed) %>% 
  mutate(across(everything(), ~replace(.x, is.nan(.x), 0)))

current.intake.impact.sims.total.allgroups<-Reduce(rbind,list.of.current.intake.impact.sims.total) %>% 
  mutate(across(everything(), ~replace(.x, is.nan(.x), 0)))
CF.intake.impact.sims.total.allgroups<-Reduce(rbind,list.of.CF.intake.impact.sims.total) %>% 
  mutate(across(everything(), ~replace(.x, is.nan(.x), 0)))
current.intake.impact.sims.consumed.allgroups<-Reduce(rbind,list.of.current.intake.impact.sims.consumed) %>% 
  mutate(across(everything(), ~replace(.x, is.nan(.x), 0)))
CF.intake.impact.sims.consumed.allgroups<-Reduce(rbind,list.of.CF.intake.impact.sims.consumed) %>% 
  mutate(across(everything(), ~replace(.x, is.nan(.x), 0)))
current.intake.impact.sims.unconsumed.allgroups<-Reduce(rbind,list.of.current.intake.impact.sims.unconsumed) %>% 
  mutate(across(everything(), ~replace(.x, is.nan(.x), 0)))
CF.intake.impact.sims.unconsumed.allgroups<-Reduce(rbind,list.of.CF.intake.impact.sims.unconsumed) %>% 
  mutate(across(everything(), ~replace(.x, is.nan(.x), 0)))

impact.sims.inedible.allgroups<-Reduce(rbind,list.of.impact.sims.inedible) %>% 
  mutate(across(everything(), ~replace(.x, is.nan(.x), 0)))
substitution.impact.sims.inedible.allgroups<-Reduce(rbind,list.of.substitution.impact.sims.inedible) %>% 
  mutate(across(everything(), ~replace(.x, is.nan(.x), 0)))
combined.impact.sims.inedible.allgroups<-Reduce(rbind,list.of.combined.impact.sims.inedible) %>% 
  mutate(across(everything(), ~replace(.x, is.nan(.x), 0)))
delta.sims.inedible.allgroups<-Reduce(rbind,list.of.delta.sims.inedible) %>% 
  mutate(across(everything(), ~replace(.x, is.nan(.x), 0)))

impact.sims.wasted.allgroups<-Reduce(rbind,list.of.impact.sims.wasted) %>% 
  mutate(across(everything(), ~replace(.x, is.nan(.x), 0)))
substitution.impact.sims.wasted.allgroups<-Reduce(rbind,list.of.substitution.impact.sims.wasted) %>% 
  mutate(across(everything(), ~replace(.x, is.nan(.x), 0)))
combined.impact.sims.wasted.allgroups<-Reduce(rbind,list.of.combined.impact.sims.wasted) %>% 
  mutate(across(everything(), ~replace(.x, is.nan(.x), 0)))
delta.sims.wasted.allgroups<-Reduce(rbind,list.of.delta.sims.wasted) %>% 
  mutate(across(everything(), ~replace(.x, is.nan(.x), 0)))

current.intake.impact.sims.inedible.allgroups<-Reduce(rbind,list.of.current.intake.impact.sims.inedible) %>% 
  mutate(across(everything(), ~replace(.x, is.nan(.x), 0)))
CF.intake.impact.sims.inedible.allgroups<-Reduce(rbind,list.of.CF.intake.impact.sims.inedible) %>% 
  mutate(across(everything(), ~replace(.x, is.nan(.x), 0)))
current.intake.impact.sims.wasted.allgroups<-Reduce(rbind,list.of.current.intake.impact.sims.wasted) %>% 
  mutate(across(everything(), ~replace(.x, is.nan(.x), 0)))
CF.intake.impact.sims.wasted.allgroups<-Reduce(rbind,list.of.CF.intake.impact.sims.wasted) %>% 
  mutate(across(everything(), ~replace(.x, is.nan(.x), 0)))
```

Save dataframes into csv files.
```{r save_files ,eval=FALSE,echo=TRUE}
#setwd("C:\\Users\\fcudhe01\\Box\\lasting_aim_3\\data\\out\\example_cost\\per_capita")
setwd(output_location)
fwrite(x=impact.sims.percapita.total.allgroups, file="per_capita/costenv.sims.percapita.granular.csv")
fwrite(x=substitution.impact.sims.percapita.total.allgroups, file="per_capita/substitution.costenv.sims.percapita.granular.csv")
fwrite(x=combined.impact.percapita.total.allgroups, file="per_capita/combined.costenv.sims.percapita.granular.csv")
fwrite(x=delta.percapita.allgroups, file="per_capita/delta.costenv.sims.percapita.granular.csv")

fwrite(x=impact.sims.percapita.consumed.allgroups, file="per_capita/costenv.sims.percapita.consumed.granular.csv")
fwrite(x=substitution.impact.sims.percapita.consumed.allgroups, file="per_capita/substitution.costenv.sims.percapita.consumed.granular.csv")
fwrite(x=combined.impact.percapita.consumed.allgroups, file="per_capita/combined.costenv.sims.percapita.consumed.granular.csv")

fwrite(x=impact.sims.percapita.unconsumed.allgroups, file="per_capita/costenv.sims.percapita.unconsumed.granular.csv")
fwrite(x=substitution.impact.sims.percapita.unconsumed.allgroups, file="per_capita/substitution.costenv.sims.percapita.unconsumed.granular.csv")
fwrite(x=combined.impact.percapita.unconsumed.allgroups, file="per_capita/combined.costenv.sims.percapita.unconsumed.granular.csv")

fwrite(x=current.intake.impact.sims.percapita.total.allgroups, file="per_capita/current.intake.costenv.sims.percapita.granular.csv")
fwrite(x=CF.intake.impact.sims.percapita.total.allgroups, file="per_capita/CF.costenv.intake.sims.percapita.granular.csv")
fwrite(x=current.intake.impact.sims.percapita.consumed.allgroups, file="per_capita/current.intake.costenv.sims.percapita.granular.consumed.csv")
fwrite(x=CF.intake.impact.sims.percapita.consumed.allgroups, file="per_capita/CF.intake.costenv.sims.percapita.granular.consumed.csv")
fwrite(x=current.intake.impact.sims.percapita.unconsumed.allgroups, file="per_capita/current.intake.costenv.sims.percapita.granular.unconsumed.csv")
fwrite(x=CF.intake.impact.sims.percapita.unconsumed.allgroups, file="per_capita/CF.intake.costenv.sims.percapita.granular.unconsumed.csv")

fwrite(x=impact.sims.percapita.consumed.allgroups, file="per_capita/costenv.sims.percapita.inedible.granular.csv")
fwrite(x=substitution.impact.sims.percapita.consumed.allgroups, file="per_capita/substitution.costenv.sims.percapita.inedible.granular.csv")
fwrite(x=combined.impact.percapita.consumed.allgroups, file="per_capita/combined.costenv.sims.percapita.inedible.granular.csv")

fwrite(x=impact.sims.percapita.consumed.allgroups, file="per_capita/costenv.sims.percapita.wasted.granular.csv")
fwrite(x=substitution.impact.sims.percapita.consumed.allgroups, file="per_capita/substitution.costenv.sims.percapita.wasted.granular.csv")
fwrite(x=combined.impact.percapita.consumed.allgroups, file="per_capita/combined.costenv.sims.percapita.wasted.granular.csv")

fwrite(x=current.intake.impact.sims.percapita.consumed.allgroups, file="per_capita/current.intake.costenv.sims.percapita.granular.inedible.csv")
fwrite(x=CF.intake.impact.sims.percapita.consumed.allgroups, file="per_capita/CF.intake.costenv.sims.percapita.granular.inedible.csv")
fwrite(x=current.intake.impact.sims.percapita.unconsumed.allgroups, file="per_capita/current.intake.costenv.sims.percapita.granular.wasted.csv")
fwrite(x=CF.intake.impact.sims.percapita.unconsumed.allgroups, file="per_capita/CF.intake.costenv.sims.percapita.granular.wasted.csv")
```

All of what we just did pertains to population level impact. Next. we get per capita sims for all outputs of interest. 

Recall there are 31 outcome types of interest, each corresponding to some combination of 1. what we are looking at (impact (as in, impact of change), substitution impact, combined impact, population, delta (aka, change in intake), current intake impact, counterfactual intake impact), and 2. level of disaggregation (total, consumed, unconsumed, inedible, wasted).
```{r per_capita_sims ,eval=FALSE,echo=TRUE}
### per capita
impact.sims.percapita.total.allgroups<-get.percapita.sims(impact.sims=impact.sims.total.allgroups, 
                                                    population.sims=population.sims.allgroups, 
                                                    pop.sims.names=paste("X", c(1:n.sims), sep=""), 
                                                    new.pop.sims.names=paste("pop", c(1:n.sims), sep=""), 
                                                    sims.names=paste("X", c(1:n.sims), sep=""))
substitution.impact.sims.percapita.total.allgroups<-get.percapita.sims(impact.sims=substitution.impact.sims.total.allgroups, 
                                                                 population.sims=population.sims.allgroups, 
                                                                 pop.sims.names=paste("X", c(1:n.sims), sep=""), 
                                                                 new.pop.sims.names=paste("pop", c(1:n.sims), sep=""), 
                                                                 sims.names=paste("X", c(1:n.sims), sep=""))
combined.impact.percapita.total.allgroups<-get.percapita.sims(impact.sims=combined.impact.sims.total.allgroups, 
                                                        population.sims=population.sims.allgroups, 
                                                        pop.sims.names=paste("X", c(1:n.sims), sep=""), 
                                                        new.pop.sims.names=paste("pop", c(1:n.sims), sep=""), 
                                                        sims.names=paste("X", c(1:n.sims), sep=""))
delta.percapita.allgroups<-get.percapita.sims(impact.sims=delta.sims.total.allgroups, 
                                              population.sims=population.sims.allgroups, 
                                              pop.sims.names=paste("X", c(1:n.sims), sep=""), 
                                              new.pop.sims.names=paste("pop", c(1:n.sims), sep=""), 
                                              sims.names=paste("X", c(1:n.sims), sep=""))

impact.sims.percapita.consumed.allgroups<-get.percapita.sims(impact.sims=impact.sims.consumed.allgroups, 
                                                    population.sims=population.sims.allgroups, 
                                                    pop.sims.names=paste("X", c(1:n.sims), sep=""), 
                                                    new.pop.sims.names=paste("pop", c(1:n.sims), sep=""), 
                                                    sims.names=paste("X", c(1:n.sims), sep=""))
substitution.impact.sims.percapita.consumed.allgroups<-get.percapita.sims(impact.sims=substitution.impact.sims.consumed.allgroups, 
                                                                 population.sims=population.sims.allgroups, 
                                                                 pop.sims.names=paste("X", c(1:n.sims), sep=""), 
                                                                 new.pop.sims.names=paste("pop", c(1:n.sims), sep=""), 
                                                                 sims.names=paste("X", c(1:n.sims), sep=""))
combined.impact.percapita.consumed.allgroups<-get.percapita.sims(impact.sims=combined.impact.sims.consumed.allgroups, 
                                                        population.sims=population.sims.allgroups, 
                                                        pop.sims.names=paste("X", c(1:n.sims), sep=""), 
                                                        new.pop.sims.names=paste("pop", c(1:n.sims), sep=""), 
                                                        sims.names=paste("X", c(1:n.sims), sep=""))

impact.sims.percapita.unconsumed.allgroups<-get.percapita.sims(impact.sims=impact.sims.unconsumed.allgroups, 
                                                             population.sims=population.sims.allgroups, 
                                                             pop.sims.names=paste("X", c(1:n.sims), sep=""), 
                                                             new.pop.sims.names=paste("pop", c(1:n.sims), sep=""), 
                                                             sims.names=paste("X", c(1:n.sims), sep=""))
substitution.impact.sims.percapita.unconsumed.allgroups<-get.percapita.sims(impact.sims=substitution.impact.sims.unconsumed.allgroups, 
                                                                          population.sims=population.sims.allgroups, 
                                                                          pop.sims.names=paste("X", c(1:n.sims), sep=""), 
                                                                          new.pop.sims.names=paste("pop", c(1:n.sims), sep=""), 
                                                                          sims.names=paste("X", c(1:n.sims), sep=""))
combined.impact.percapita.unconsumed.allgroups<-get.percapita.sims(impact.sims=combined.impact.sims.unconsumed.allgroups, 
                                                                 population.sims=population.sims.allgroups, 
                                                                 pop.sims.names=paste("X", c(1:n.sims), sep=""), 
                                                                 new.pop.sims.names=paste("pop", c(1:n.sims), sep=""), 
                                                                 sims.names=paste("X", c(1:n.sims), sep=""))


current.intake.impact.sims.percapita.total.allgroups<-get.percapita.sims(impact.sims=current.intake.impact.sims.total.allgroups, 
                                                          population.sims=population.sims.allgroups, 
                                                          pop.sims.names=paste("X", c(1:n.sims), sep=""), 
                                                          new.pop.sims.names=paste("pop", c(1:n.sims), sep=""), 
                                                          sims.names=paste("X", c(1:n.sims), sep=""))
CF.intake.impact.sims.percapita.total.allgroups<-get.percapita.sims(impact.sims=CF.intake.impact.sims.total.allgroups, 
                                                             population.sims=population.sims.allgroups,  
                                                             pop.sims.names=paste("X", c(1:n.sims), sep=""), 
                                                             new.pop.sims.names=paste("pop", c(1:n.sims), sep=""), 
                                                             sims.names=paste("X", c(1:n.sims), sep=""))
current.intake.impact.sims.percapita.consumed.allgroups<-get.percapita.sims(impact.sims=current.intake.impact.sims.consumed.allgroups, 
                                                                         population.sims=population.sims.allgroups, 
                                                                         pop.sims.names=paste("X", c(1:n.sims), sep=""), 
                                                                         new.pop.sims.names=paste("pop", c(1:n.sims), sep=""), 
                                                                         sims.names=paste("X", c(1:n.sims), sep=""))
CF.intake.impact.sims.percapita.consumed.allgroups<-get.percapita.sims(impact.sims=CF.intake.impact.sims.consumed.allgroups, 
                                                                    population.sims=population.sims.allgroups, 
                                                                    pop.sims.names=paste("X", c(1:n.sims), sep=""), 
                                                                    new.pop.sims.names=paste("pop", c(1:n.sims), sep=""), 
                                                                    sims.names=paste("X", c(1:n.sims), sep=""))
current.intake.impact.sims.percapita.unconsumed.allgroups<-get.percapita.sims(impact.sims=current.intake.impact.sims.unconsumed.allgroups, 
                                                                            population.sims=population.sims.allgroups, 
                                                                            pop.sims.names=paste("X", c(1:n.sims), sep=""), 
                                                                            new.pop.sims.names=paste("pop", c(1:n.sims), sep=""), 
                                                                            sims.names=paste("X", c(1:n.sims), sep=""))
CF.intake.impact.sims.percapita.unconsumed.allgroups<-get.percapita.sims(impact.sims=CF.intake.impact.sims.unconsumed.allgroups, 
                                                                       population.sims=population.sims.allgroups, 
                                                                       pop.sims.names=paste("X", c(1:n.sims), sep=""), 
                                                                       new.pop.sims.names=paste("pop", c(1:n.sims), sep=""), 
                                                                       sims.names=paste("X", c(1:n.sims), sep=""))


impact.sims.percapita.inedible.allgroups<-get.percapita.sims(impact.sims=impact.sims.inedible.allgroups, 
                                                               population.sims=population.sims.allgroups, 
                                                               pop.sims.names=paste("X", c(1:n.sims), sep=""), 
                                                               new.pop.sims.names=paste("pop", c(1:n.sims), sep=""), 
                                                               sims.names=paste("X", c(1:n.sims), sep=""))
substitution.impact.sims.percapita.inedible.allgroups<-get.percapita.sims(impact.sims=substitution.impact.sims.inedible.allgroups, 
                                                                            population.sims=population.sims.allgroups, 
                                                                            pop.sims.names=paste("X", c(1:n.sims), sep=""), 
                                                                            new.pop.sims.names=paste("pop", c(1:n.sims), sep=""), 
                                                                            sims.names=paste("X", c(1:n.sims), sep=""))
combined.impact.percapita.inedible.allgroups<-get.percapita.sims(impact.sims=combined.impact.sims.inedible.allgroups, 
                                                                   population.sims=population.sims.allgroups, 
                                                                   pop.sims.names=paste("X", c(1:n.sims), sep=""), 
                                                                   new.pop.sims.names=paste("pop", c(1:n.sims), sep=""), 
                                                                   sims.names=paste("X", c(1:n.sims), sep=""))

impact.sims.percapita.wasted.allgroups<-get.percapita.sims(impact.sims=impact.sims.wasted.allgroups, 
                                                             population.sims=population.sims.allgroups, 
                                                             pop.sims.names=paste("X", c(1:n.sims), sep=""), 
                                                             new.pop.sims.names=paste("pop", c(1:n.sims), sep=""), 
                                                             sims.names=paste("X", c(1:n.sims), sep=""))
substitution.impact.sims.percapita.wasted.allgroups<-get.percapita.sims(impact.sims=substitution.impact.sims.wasted.allgroups, 
                                                                          population.sims=population.sims.allgroups, 
                                                                          pop.sims.names=paste("X", c(1:n.sims), sep=""), 
                                                                          new.pop.sims.names=paste("pop", c(1:n.sims), sep=""), 
                                                                          sims.names=paste("X", c(1:n.sims), sep=""))
combined.impact.percapita.wasted.allgroups<-get.percapita.sims(impact.sims=combined.impact.sims.wasted.allgroups, 
                                                                 population.sims=population.sims.allgroups, 
                                                                 pop.sims.names=paste("X", c(1:n.sims), sep=""), 
                                                                 new.pop.sims.names=paste("pop", c(1:n.sims), sep=""), 
                                                                 sims.names=paste("X", c(1:n.sims), sep=""))

current.intake.impact.sims.percapita.inedible.allgroups<-get.percapita.sims(impact.sims=current.intake.impact.sims.inedible.allgroups, 
                                                                            population.sims=population.sims.allgroups, 
                                                                            pop.sims.names=paste("X", c(1:n.sims), sep=""), 
                                                                            new.pop.sims.names=paste("pop", c(1:n.sims), sep=""), 
                                                                            sims.names=paste("X", c(1:n.sims), sep=""))
CF.intake.impact.sims.percapita.inedible.allgroups<-get.percapita.sims(impact.sims=CF.intake.impact.sims.inedible.allgroups, 
                                                                       population.sims=population.sims.allgroups, 
                                                                       pop.sims.names=paste("X", c(1:n.sims), sep=""), 
                                                                       new.pop.sims.names=paste("pop", c(1:n.sims), sep=""), 
                                                                       sims.names=paste("X", c(1:n.sims), sep=""))
current.intake.impact.sims.percapita.wasted.allgroups<-get.percapita.sims(impact.sims=current.intake.impact.sims.wasted.allgroups, 
                                                                              population.sims=population.sims.allgroups, 
                                                                              pop.sims.names=paste("X", c(1:n.sims), sep=""), 
                                                                              new.pop.sims.names=paste("pop", c(1:n.sims), sep=""), 
                                                                              sims.names=paste("X", c(1:n.sims), sep=""))
CF.intake.impact.sims.percapita.wasted.allgroups<-get.percapita.sims(impact.sims=CF.intake.impact.sims.wasted.allgroups, 
                                                                         population.sims=population.sims.allgroups, 
                                                                         pop.sims.names=paste("X", c(1:n.sims), sep=""), 
                                                                         new.pop.sims.names=paste("pop", c(1:n.sims), sep=""), 
                                                                         sims.names=paste("X", c(1:n.sims), sep=""))

```

Save them into csv files.
```{r save_per_capita_sims, eval=FALSE,echo=TRUE}
#setwd("C:\\Users\\fcudhe01\\Box\\lasting_aim_3\\data\\out\\example_cost\\per_capita")
setwd(output_location)
fwrite(x=impact.sims.percapita.total.allgroups, file="per_capita/costenv.sims.percapita.granular.csv")
fwrite(x=substitution.impact.sims.percapita.total.allgroups, file="per_capita/substitution.costenv.sims.percapita.granular.csv")
fwrite(x=combined.impact.percapita.total.allgroups, file="per_capita/combined.costenv.sims.percapita.granular.csv")
fwrite(x=delta.percapita.allgroups, file="per_capita/delta.costenv.sims.percapita.granular.csv")

fwrite(x=impact.sims.percapita.consumed.allgroups, file="per_capita/costenv.sims.percapita.consumed.granular.csv")
fwrite(x=substitution.impact.sims.percapita.consumed.allgroups, file="per_capita/substitution.costenv.sims.percapita.consumed.granular.csv")
fwrite(x=combined.impact.percapita.consumed.allgroups, file="per_capita/combined.costenv.sims.percapita.consumed.granular.csv")

fwrite(x=impact.sims.percapita.unconsumed.allgroups, file="per_capita/costenv.sims.percapita.unconsumed.granular.csv")
fwrite(x=substitution.impact.sims.percapita.unconsumed.allgroups, file="per_capita/substitution.costenv.sims.percapita.unconsumed.granular.csv")
fwrite(x=combined.impact.percapita.unconsumed.allgroups, file="per_capita/combined.costenv.sims.percapita.unconsumed.granular.csv")

fwrite(x=current.intake.impact.sims.percapita.total.allgroups, file="per_capita/current.intake.costenv.sims.percapita.granular.csv")
fwrite(x=CF.intake.impact.sims.percapita.total.allgroups, file="per_capita/CF.costenv.intake.sims.percapita.granular.csv")
fwrite(x=current.intake.impact.sims.percapita.consumed.allgroups, file="per_capita/current.intake.costenv.sims.percapita.granular.consumed.csv")
fwrite(x=CF.intake.impact.sims.percapita.consumed.allgroups, file="per_capita/CF.intake.costenv.sims.percapita.granular.consumed.csv")
fwrite(x=current.intake.impact.sims.percapita.unconsumed.allgroups, file="per_capita/current.intake.costenv.sims.percapita.granular.unconsumed.csv")
fwrite(x=CF.intake.impact.sims.percapita.unconsumed.allgroups, file="per_capita/CF.intake.costenv.sims.percapita.granular.unconsumed.csv")

fwrite(x=impact.sims.percapita.consumed.allgroups, file="per_capita/costenv.sims.percapita.inedible.granular.csv")
fwrite(x=substitution.impact.sims.percapita.consumed.allgroups, file="per_capita/substitution.costenv.sims.percapita.inedible.granular.csv")
fwrite(x=combined.impact.percapita.consumed.allgroups, file="per_capita/combined.costenv.sims.percapita.inedible.granular.csv")

fwrite(x=impact.sims.percapita.consumed.allgroups, file="per_capita/costenv.sims.percapita.wasted.granular.csv")
fwrite(x=substitution.impact.sims.percapita.consumed.allgroups, file="per_capita/substitution.costenv.sims.percapita.wasted.granular.csv")
fwrite(x=combined.impact.percapita.consumed.allgroups, file="per_capita/combined.costenv.sims.percapita.wasted.granular.csv")

fwrite(x=current.intake.impact.sims.percapita.consumed.allgroups, file="per_capita/current.intake.costenv.sims.percapita.granular.inedible.csv")
fwrite(x=CF.intake.impact.sims.percapita.consumed.allgroups, file="per_capita/CF.intake.costenv.sims.percapita.granular.inedible.csv")
fwrite(x=current.intake.impact.sims.percapita.unconsumed.allgroups, file="per_capita/current.intake.costenv.sims.percapita.granular.wasted.csv")
fwrite(x=CF.intake.impact.sims.percapita.unconsumed.allgroups, file="per_capita/CF.intake.costenv.sims.percapita.granular.wasted.csv")
```

Get summary stats from simulations (mean, median, standard deviation, uncertainty intervals, the things you'll be reporting in your manuscript) for all outcome of interests and save (for both total and per capita impact).
```{r summaraize, eval=FALSE,echo=TRUE}
################
##get summary stats 
#############
all.impact.sims.summary<-get.summary.stats(impact.sims=impact.sims.total.allgroups, 
                                           substitution.impact.sims=substitution.impact.sims.total.allgroups, 
                                           combined.impact.sims=combined.impact.sims.total.allgroups, 
                                           delta.sims=delta.sims.total.allgroups, 
                                           impact.sims.consumed=impact.sims.consumed.allgroups, 
                                           substitution.impact.sims.consumed=substitution.impact.sims.consumed.allgroups, 
                                           combined.impact.sims.consumed=combined.impact.sims.consumed.allgroups,
                                           impact.sims.unconsumed=impact.sims.unconsumed.allgroups, 
                                           substitution.impact.sims.unconsumed=substitution.impact.sims.unconsumed.allgroups, 
                                           combined.impact.sims.unconsumed=combined.impact.sims.unconsumed.allgroups, 
                                           current.intake.impact.sims=current.intake.impact.sims.total.allgroups, 
                                           current.intake.impact.sims.consumed=current.intake.impact.sims.consumed.allgroups, 
                                           current.intake.impact.sims.unconsumed=current.intake.impact.sims.unconsumed.allgroups, 
                                           CF.intake.impact.sims=CF.intake.impact.sims.total.allgroups, 
                                           CF.intake.impact.sims.consumed=CF.intake.impact.sims.consumed.allgroups, 
                                           CF.intake.impact.sims.unconsumed=CF.intake.impact.sims.unconsumed.allgroups,
                                           impact.sims.inedible=impact.sims.inedible.allgroups, 
                                           substitution.impact.sims.inedible=substitution.impact.sims.inedible.allgroups, 
                                           combined.impact.sims.inedible=combined.impact.sims.inedible.allgroups,
                                           impact.sims.wasted=impact.sims.wasted.allgroups, 
                                           substitution.impact.sims.wasted=substitution.impact.sims.wasted.allgroups, 
                                           combined.impact.sims.wasted=combined.impact.sims.wasted.allgroups, 
                                           current.intake.impact.sims.inedible=current.intake.impact.sims.inedible.allgroups, 
                                           current.intake.impact.sims.wasted=current.intake.impact.sims.wasted.allgroups, 
                                           CF.intake.impact.sims.inedible=CF.intake.impact.sims.inedible.allgroups, 
                                           CF.intake.impact.sims.wasted=CF.intake.impact.sims.wasted.allgroups,
                                           vars=paste("X", 1:n.sims, sep=""))
#setwd("C:\\Users\\fcudhe01\\Box\\lasting_aim_3\\data\\out\\example_cost")
setwd(output_location)
write.csv(x=all.impact.sims.summary, file="costenv.summary.granular.csv")

##
#now use the function for per capita results
all.impact.sims.percapita.summary<-get.summary.stats(impact.sims=impact.sims.percapita.total.allgroups, 
                                                     substitution.impact.sims=substitution.impact.sims.percapita.total.allgroups, 
                                                     combined.impact.sims=combined.impact.percapita.total.allgroups,
                                                     delta.sims=delta.percapita.allgroups, 
                                                     impact.sims.consumed=impact.sims.percapita.consumed.allgroups, 
                                                     substitution.impact.sims.consumed=substitution.impact.sims.percapita.unconsumed.allgroups, 
                                                     combined.impact.sims.consumed=combined.impact.percapita.unconsumed.allgroups,
                                                     impact.sims.unconsumed=impact.sims.percapita.unconsumed.allgroups, 
                                                     substitution.impact.sims.unconsumed=substitution.impact.sims.percapita.unconsumed.allgroups, 
                                                     combined.impact.sims.unconsumed=combined.impact.percapita.unconsumed.allgroups, 
                                                     current.intake.impact.sims=current.intake.impact.sims.percapita.total.allgroups, 
                                                     current.intake.impact.sims.consumed=current.intake.impact.sims.percapita.consumed.allgroups, 
                                                     current.intake.impact.sims.unconsumed=current.intake.impact.sims.percapita.unconsumed.allgroups, 
                                                     CF.intake.impact.sims=CF.intake.impact.sims.total.allgroups, 
                                                     CF.intake.impact.sims.consumed=CF.intake.impact.sims.percapita.consumed.allgroups, 
                                                     CF.intake.impact.sims.unconsumed=CF.intake.impact.sims.percapita.unconsumed.allgroups,
                                                     impact.sims.inedible=impact.sims.percapita.inedible.allgroups, 
                                                     substitution.impact.sims.inedible=substitution.impact.sims.percapita.inedible.allgroups, 
                                                     combined.impact.sims.inedible=combined.impact.percapita.inedible.allgroups,
                                                     impact.sims.wasted=impact.sims.percapita.wasted.allgroups, 
                                                     substitution.impact.sims.wasted=substitution.impact.sims.percapita.wasted.allgroups, 
                                                     combined.impact.sims.wasted=combined.impact.percapita.wasted.allgroups,
                                                     current.intake.impact.sims.inedible=current.intake.impact.sims.percapita.inedible.allgroups, 
                                                     current.intake.impact.sims.wasted=current.intake.impact.sims.percapita.wasted.allgroups, 
                                                     CF.intake.impact.sims.inedible=CF.intake.impact.sims.percapita.inedible.allgroups, 
                                                     CF.intake.impact.sims.wasted=CF.intake.impact.sims.percapita.wasted.allgroups,
                                                     vars=paste("X", 1:n.sims, sep=""))
#setwd("C:\\Users\\fcudhe01\\Box\\lasting_aim_3\\data\\out\\example_cost\\per_capita")
setwd(output_location)
write.csv(x=all.impact.sims.percapita.summary, file="per_capita/costenv.percapita.summary.granular.csv")
```

Next, we want to get summary stat for all possible strata combinations (not just the most granular, age/sex/race/foodgroup).

First we create a list of all possible strata combinations. Note, the string vector "strata" contains all the strata being used for the analysis. If you want to use different strata, you need to change the line defining "strata" accordingly. 

```{r define_strata_combos, eval=FALSE,echo=TRUE}
##########get sums based on less granular subgroups#########
##get all possible combinations of strata
strata<-c("age_gp", "sex_gp", "race_gp", "Foodgroup")

strata.combos<-list()
for(i in 1:length(strata))
{
  x<-combn(strata, i)
  combos.for.i<-split(x, rep(1:ncol(x), each = nrow(x))) #https://stackoverflow.com/questions/6819804/how-to-convert-a-matrix-to-a-list-of-column-vectors-in-r
  strata.combos<-c(strata.combos, combos.for.i)
}
strata.combos["null"]<-list(NULL) ##add null element to list to use for overall numbers
```

Get summary stats by all strata combinations for all outcomes of interest. Note that the objects being created here are lists of lists. The second level are the different strata combinations. The first level denotes outcome type: 1 = total summary stats, 2 = total sims, 3 = per capita summary stats, 4 = per capita sims. That means, for example, that summ.stats.by.strata.cost is a list, and each element within that list is also a list. Specifically, it is a list of 4 lists (each one denoting outcome type), and each of those 4 lists is itself a list of 48 data frames, one for each subgroup. 
```{r geta_sum_stats_by_strata_combos, eval=FALSE,echo=TRUE}
# summary.stats.by.strata<-function(impact.sims.allgroups, strata.combos.list, pop.sims)
# {
#   cols.to.sum<-paste("X", 1:n.sims, sep="")
#   pop.cols.to.sum<-paste("pop", 1:n.sims, sep="")
#   
#   sims.data.table<-as.data.table(impact.sims.allgroups)
#   pop.sims.data.table<-as.data.table(pop.sims)
#   
#   strata.combos.sims<-list()
#   strata.combos.sims.long<-list()
#   strata.combos.summary.stats.long<-list()
#   strata.combos.summary.stats.wide<-list()
#   
#   pop.strata.combos.sims<-list() 
#   
#   percapita.sims<-list()
#   percapita.sims.long<-list()
#   percapita.summary.stats.long<-list()
#   percapita.summary.stats.wide<-list()
#   
#   for(j in 1:length(strata.combos))
#   {
#     labels<-c(strata.combos[[j]], "intake_units", "outcome", "outcome_unit")
#     
#     strata.combos.sims[[j]]<-sims.data.table[,lapply(.SD, sum), by=c(strata.combos[[j]], "intake_units", "outcome", "outcome_unit"), 
#                                              .SDcols=cols.to.sum]
#     
#     pop.strata<-strata.combos[[j]][!(strata.combos[[j]] %in% c("Foodgroup", "broad_foodgroup"))]
#     
#     if(is.null(pop.strata))
#     {
#       pop.strata.combos.sims[[j]]<-pop.sims.data.table[,lapply(.SD, sum), .SDcols=cols.to.sum]
#     }else
#     {
#       pop.strata.combos.sims[[j]]<-pop.sims.data.table[,lapply(.SD, sum), by=c(pop.strata), .SDcols=cols.to.sum]
#     }
#     names(pop.strata.combos.sims[[j]])<-gsub(x=names(pop.strata.combos.sims[[j]]), pattern="X", replacement="pop")
#     
#     if(length(intersect(names(strata.combos.sims[[j]]), names(pop.strata.combos.sims[[j]])))==0)
#     {
#       merged<-cbind(strata.combos.sims[[j]], pop.strata.combos.sims[[j]])
#     }
#     if(length(intersect(names(strata.combos.sims[[j]]), names(pop.strata.combos.sims[[j]])))!=0)
#     {
#       merged<-merge(strata.combos.sims[[j]], pop.strata.combos.sims[[j]])
#     }
#     
#     
#     merged.names<-merged[,..labels]
#     percapita.sims[[j]]<-merged[,..cols.to.sum]/merged[,..pop.cols.to.sum]
#     percapita.sims[[j]]<-cbind(merged.names, percapita.sims[[j]])
#     
#     strata.combos.sims.long[[j]]<-melt(strata.combos.sims[[j]], id.vars = c(strata.combos[[j]], "intake_units", "outcome", "outcome_unit"), measure.vars=cols.to.sum)
#     strata.combos.summary.stats.long[[j]]<-strata.combos.sims.long[[j]][, .(quantile(value, c(.025, .5, .975))), by=c(strata.combos[[j]], "intake_units", "outcome", "outcome_unit")]
#     strata.combos.summary.stats.long[[j]]<-cbind(strata.combos.summary.stats.long[[j]], 
#                                                  as.factor(rep(c("lower_bound (2.5th percentile)", "median", "upper_bound  (97.5th percentile)"), dim(strata.combos.summary.stats.long[[j]])[1]/3)))
#     #strata.combos.summary.stats.wide[[j]]<-dcast(strata.combos.summary.stats.long[[j]], "Comorbid_count + Insurance + Race ~ V2", value.var="V1")
#     strata.combos.summary.stats.wide[[j]]<-dcast(strata.combos.summary.stats.long[[j]], paste(paste(strata.combos[[j]], collapse=' + '), "+ intake_units + outcome + outcome_unit", " ~ V2", sep=""),
#                                                  value.var="V1")    
#     
#     ##nperhaps in future, make it so that the function doesn't rely on specific names for intake_units, outcome, outcome_unit 
#     
#     percapita.sims.long[[j]]<-melt(percapita.sims[[j]], id.vars = c(strata.combos[[j]], "intake_units", "outcome", "outcome_unit"), measure.vars=cols.to.sum)
#     percapita.summary.stats.long[[j]]<-percapita.sims.long[[j]][, .(quantile(value, c(.025, .5, .975))), by=c(strata.combos[[j]], "intake_units", "outcome", "outcome_unit")]
#     percapita.summary.stats.long[[j]]<-cbind(percapita.summary.stats.long[[j]], 
#                                              as.factor(rep(c("lower_bound (2.5th percentile)", "median", "upper_bound  (97.5th percentile)"), 
#                                                            dim(percapita.summary.stats.long[[j]])[1]/3)))
#     #strata.combos.summary.stats.wide[[j]]<-dcast(strata.combos.summary.stats.long[[j]], "Comorbid_count + Insurance + Race ~ V2", value.var="V1")
#     percapita.summary.stats.wide[[j]]<-dcast(percapita.summary.stats.long[[j]], paste(paste(strata.combos[[j]], collapse=' + '), " + intake_units + outcome + outcome_unit", " ~ V2", sep=""),
#                                              value.var="V1")    
#     
#     
#   }
#   
#   return(list("summary.output" = strata.combos.summary.stats.wide, 
#               "full.sims.output" = strata.combos.sims,
#               "summary.output.percapita"= percapita.summary.stats.wide,
#               "full.sims.output.percapita" = percapita.sims)
#   )
# }

setwd(paste(output_location, "/By_SubGroup", sep=""))
summ.stats.by.strata.cost<-summary.stats.by.strata(impact.sims.allgroups=impact.sims.total.allgroups, 
                                                   strata.combos.list=strata.combos, 
                                                   pop.sims=pop.sims)
summ.stats.by.strata.substitution.cost<-summary.stats.by.strata(impact.sims.allgroups=substitution.impact.sims.total.allgroups, 
                                                                strata.combos.list=strata.combos, 
                                                                pop.sims=pop.sims)
summ.stats.by.strata.combined.cost<-summary.stats.by.strata(impact.sims.allgroups=combined.impact.sims.total.allgroups, 
                                                            strata.combos.list=strata.combos, 
                                                            pop.sims=pop.sims)
summ.stats.by.strata.delta_forcost<-summary.stats.by.strata(impact.sims.allgroups=delta.sims.total.allgroups, 
                                                            strata.combos.list=strata.combos, 
                                                            pop.sims=pop.sims)

summ.stats.by.strata.combined.consumed.cost<-summary.stats.by.strata(impact.sims.allgroups=combined.impact.sims.consumed.allgroups, 
                                                            strata.combos.list=strata.combos, 
                                                            pop.sims=pop.sims)
summ.stats.by.strata.combined.unconsumed.cost<-summary.stats.by.strata(impact.sims.allgroups=combined.impact.sims.unconsumed.allgroups, 
                                                            strata.combos.list=strata.combos, 
                                                            pop.sims=pop.sims)

summ.stats.by.strata.current.intake.cost<-summary.stats.by.strata(impact.sims.allgroups=current.intake.impact.sims.total.allgroups, 
                                                                    strata.combos.list=strata.combos, 
                                                                    pop.sims=pop.sims)
summ.stats.by.strata.CF.intake.cost<-summary.stats.by.strata(impact.sims.allgroups=CF.intake.impact.sims.total.allgroups, 
                                                                       strata.combos.list=strata.combos, 
                                                                       pop.sims=pop.sims)
summ.stats.by.strata.current.intake.consumed.cost<-summary.stats.by.strata(impact.sims.allgroups=current.intake.impact.sims.consumed.allgroups, 
                                                                  strata.combos.list=strata.combos, 
                                                                  pop.sims=pop.sims)
summ.stats.by.strata.CF.intake.consumed.cost<-summary.stats.by.strata(impact.sims.allgroups=CF.intake.impact.sims.consumed.allgroups, 
                                                             strata.combos.list=strata.combos, 
                                                             pop.sims=pop.sims)
summ.stats.by.strata.current.intake.unconsumed.cost<-summary.stats.by.strata(impact.sims.allgroups=current.intake.impact.sims.unconsumed.allgroups, 
                                                                           strata.combos.list=strata.combos, 
                                                                           pop.sims=pop.sims)
summ.stats.by.strata.CF.intake.unconsumed.cost<-summary.stats.by.strata(impact.sims.allgroups=CF.intake.impact.sims.unconsumed.allgroups, 
                                                                      strata.combos.list=strata.combos, 
                                                                      pop.sims=pop.sims)

##inedible and wasted
summ.stats.by.strata.combined.inedible.cost<-summary.stats.by.strata(impact.sims.allgroups=combined.impact.sims.inedible.allgroups, 
                                                                     strata.combos.list=strata.combos, 
                                                                     pop.sims=pop.sims)
summ.stats.by.strata.combined.wasted.cost<-summary.stats.by.strata(impact.sims.allgroups=combined.impact.sims.wasted.allgroups, 
                                                                       strata.combos.list=strata.combos, 
                                                                       pop.sims=pop.sims)

summ.stats.by.strata.current.intake.inedible.cost<-summary.stats.by.strata(impact.sims.allgroups=current.intake.impact.sims.inedible.allgroups, 
                                                                           strata.combos.list=strata.combos, 
                                                                           pop.sims=pop.sims)
summ.stats.by.strata.CF.intake.inedible.cost<-summary.stats.by.strata(impact.sims.allgroups=CF.intake.impact.sims.inedible.allgroups, 
                                                                      strata.combos.list=strata.combos, 
                                                                      pop.sims=pop.sims)
summ.stats.by.strata.current.intake.wasted.cost<-summary.stats.by.strata(impact.sims.allgroups=current.intake.impact.sims.wasted.allgroups, 
                                                                             strata.combos.list=strata.combos, 
                                                                             pop.sims=pop.sims)
summ.stats.by.strata.CF.intake.wasted.cost<-summary.stats.by.strata(impact.sims.allgroups=CF.intake.impact.sims.wasted.allgroups, 
                                                                        strata.combos.list=strata.combos, 
                                                                        pop.sims=pop.sims)
```

Next, we're going to go through a for loop and output all outcomes into their own csv files for each strata combination (In my opinion, this is a better way to go about it than manually saving each file. Less prone to error, and robust to future changes). 

First, start the for loop
```{r output_strata_combos_start_for_loop, eval=FALSE,echo=TRUE}
for(j in 1:length(strata.combos))
{
```

In loop: First, save full sim outputs for total and per capita
```{r save_full_sims, eval=FALSE,echo=TRUE}
  setwd(paste(output_location, "/By_SubGroup/full_sims", sep=""))
  #setwd("C:\\Users\\fcudhe01\\Box\\lasting_aim_3\\data\\out\\example_cost\\BySubGroup\\full_sims")
  fwrite(x=summ.stats.by.strata.cost[[2]][[j]], file=paste("full.costenv.sims.output_by_", paste(strata.combos[[j]], collapse='_'), ".csv", sep=""))
  fwrite(x=summ.stats.by.strata.substitution.cost[[2]][[j]], file=paste("full.costenv.sims.substitution.output_by_", paste(strata.combos[[j]], collapse='_'), ".csv", sep=""))
  fwrite(x=summ.stats.by.strata.combined.cost[[2]][[j]], file=paste("full.costenv.sims.combined.output_by_", paste(strata.combos[[j]], collapse='_'), ".csv", sep=""))
  
  setwd(paste(output_location, "/per_capita/By_SubGroup/full_sims", sep=""))
  #setwd("C:\\Users\\fcudhe01\\Box\\lasting_aim_3\\data\\out\\example_cost\\per_capita\\BySubGroup\\full_sims")
  fwrite(x=summ.stats.by.strata.cost[[4]][[j]], file=paste("full.costenv.sims.percapita.output_by_", paste(strata.combos[[j]], collapse='_'), ".csv", sep=""))
  fwrite(x=summ.stats.by.strata.substitution.cost[[4]][[j]], file=paste("full.costenv.sims.percapita.substitution.output_by_", paste(strata.combos[[j]], collapse='_'), ".csv", sep=""))
  fwrite(x=summ.stats.by.strata.combined.cost[[4]][[j]], file=paste("full.costenv.sims.percapita.combined.output_by_", paste(strata.combos[[j]], collapse='_'), ".csv", sep=""))
```

Still in loop: Next, create outcome names to be used as variable names, and put relevant outcome data frames into two lists (for total and per capita). Within the k-loop, the summary stat variable names for the dataframes listed in outcome.data" are being changed so that they all consistently use the naming convention outlined in "outcome.names". 
```{r outcome_names, eval=FALSE,echo=TRUE}
  #need to edit all this renaming code so it renames the new mean and SD columns. Perhaps take the oppurtunity to make it more code effiicent by
  ## havinga set vector to rename, and using cat to combine the var name and the old name to create new name.
  
  to.rename<-c("lower_bound (2.5th percentile)", "median", "upper_bound  (97.5th percentile)", "mean", "SD")
  outcome.names<-c("impact", 
                   "substitution_impact", 
                   "combined_impact", 
                   "delta", 
                   "combined_consumed_impact", 
                   "combined_unconsumed_impact", 
                   "current_intake_impact", 
                   "CF_intake_impact", 
                   "current_intake_consumed_impact", 
                   "CF_intake_consumed_impact", 
                   "current_intake_unconsumed_impact", 
                   "CF_intake_unconsumed_impact",
                   ##inedible, wasted
                   "combined_inedible_impact", 
                   "combined_wasted_impact", 
                   "current_intake_inedible_impact", 
                   "CF_intake_inedible_impact", 
                   "current_intake_wasted_impact", 
                   "CF_intake_wasted_impact"
                   )
  outcome.data<-list(summ.stats.by.strata.cost[[1]][[j]],
                     summ.stats.by.strata.substitution.cost[[1]][[j]],
                     summ.stats.by.strata.combined.cost[[1]][[j]],
                     summ.stats.by.strata.delta_forcost[[1]][[j]],
                     summ.stats.by.strata.combined.consumed.cost[[1]][[j]],
                     summ.stats.by.strata.combined.unconsumed.cost[[1]][[j]],
                     summ.stats.by.strata.current.intake.cost[[1]][[j]],
                     summ.stats.by.strata.CF.intake.cost[[1]][[j]],
                     summ.stats.by.strata.current.intake.consumed.cost[[1]][[j]],
                     summ.stats.by.strata.CF.intake.consumed.cost[[1]][[j]],
                     summ.stats.by.strata.current.intake.unconsumed.cost[[1]][[j]],
                     summ.stats.by.strata.CF.intake.unconsumed.cost[[1]][[j]],
                     ##inedible, wasted
                     summ.stats.by.strata.combined.inedible.cost[[1]][[j]],
                     summ.stats.by.strata.combined.wasted.cost[[1]][[j]],
                     summ.stats.by.strata.current.intake.inedible.cost[[1]][[j]],
                     summ.stats.by.strata.CF.intake.inedible.cost[[1]][[j]],
                     summ.stats.by.strata.current.intake.wasted.cost[[1]][[j]],
                     summ.stats.by.strata.CF.intake.wasted.cost[[1]][[j]]
                     )
 outcome.data.per.capita<-list(summ.stats.by.strata.cost[[3]][[j]],
                     summ.stats.by.strata.substitution.cost[[3]][[j]],
                     summ.stats.by.strata.combined.cost[[3]][[j]],
                     summ.stats.by.strata.delta_forcost[[3]][[j]],
                     summ.stats.by.strata.combined.consumed.cost[[3]][[j]],
                     summ.stats.by.strata.combined.unconsumed.cost[[3]][[j]],
                     summ.stats.by.strata.current.intake.cost[[3]][[j]],
                     summ.stats.by.strata.CF.intake.cost[[3]][[j]],
                     summ.stats.by.strata.current.intake.consumed.cost[[3]][[j]],
                     summ.stats.by.strata.CF.intake.consumed.cost[[3]][[j]],
                     summ.stats.by.strata.current.intake.unconsumed.cost[[3]][[j]],
                     summ.stats.by.strata.CF.intake.unconsumed.cost[[3]][[j]],
                     ##inedible, wasted
                     summ.stats.by.strata.combined.inedible.cost[[3]][[j]],
                     summ.stats.by.strata.combined.wasted.cost[[3]][[j]],
                     summ.stats.by.strata.current.intake.inedible.cost[[3]][[j]],
                     summ.stats.by.strata.CF.intake.inedible.cost[[3]][[j]],
                     summ.stats.by.strata.current.intake.wasted.cost[[3]][[j]],
                     summ.stats.by.strata.CF.intake.wasted.cost[[3]][[j]]
  )
  
  for(k in 1:length(outcome.names))
  {
   names(outcome.data[[k]])[which(names(outcome.data[[k]]) %in% c("lower_bound (2.5th percentile)", "median", "upper_bound  (97.5th percentile)", "mean", "SD"))]<-
     paste(outcome.names[k], c("lower_bound (2.5th percentile)", "median", "upper_bound  (97.5th percentile)", "mean", "SD"), sep="_")
   names(outcome.data.per.capita[[k]])[which(names(outcome.data.per.capita[[k]]) %in% c("lower_bound (2.5th percentile)", "median", "upper_bound  (97.5th percentile)", "mean", "SD"))]<-
     paste(outcome.names[k], c("lower_bound (2.5th percentile)", "median", "upper_bound  (97.5th percentile)", "mean", "SD"), sep="_")
  }
  
  # names(summ.stats.by.strata.cost[[1]][[j]])[which(names(summ.stats.by.strata.cost[[1]][[j]]) %in% c("lower_bound (2.5th percentile)", "median", "upper_bound  (97.5th percentile)"))]<-
  #   c("impact_lower_bound (2.5th percentile)", "impact_median", "impact_upper_bound  (97.5th percentile)")
  # names(summ.stats.by.strata.substitution.cost[[1]][[j]])[which(names(summ.stats.by.strata.substitution.cost[[1]][[j]]) %in% c("lower_bound (2.5th percentile)", "median", "upper_bound  (97.5th percentile)"))]<-
  #   c("substitution_impact_lower_bound (2.5th percentile)", "substitution_impact_median", "substitution_impact_upper_bound  (97.5th percentile)")
  # names(summ.stats.by.strata.combined.cost[[1]][[j]])[which(names(summ.stats.by.strata.combined.cost[[1]][[j]]) %in% c("lower_bound (2.5th percentile)", "median", "upper_bound  (97.5th percentile)"))]<-
  #   c("combined_impact_lower_bound (2.5th percentile)", "combined_impact_median", "combined_impact_upper_bound  (97.5th percentile)")
  # names(summ.stats.by.strata.delta_forcost[[1]][[j]])[which(names(summ.stats.by.strata.delta_forcost[[1]][[j]]) %in% c("lower_bound (2.5th percentile)", "median", "upper_bound  (97.5th percentile)"))]<-
  #   c("delta_lower_bound (2.5th percentile)", "delta_median", "delta_upper_bound  (97.5th percentile)")
  # names(summ.stats.by.strata.combined.consumed.cost[[1]][[j]])[which(names(summ.stats.by.strata.combined.consumed.cost[[1]][[j]]) %in% c("lower_bound (2.5th percentile)", "median", "upper_bound  (97.5th percentile)"))]<-
  #   c("combined_consumed_impact_lower_bound (2.5th percentile)", "combined_consumed_impact_median", "combined_consumed_impact_upper_bound  (97.5th percentile)")
  # names(summ.stats.by.strata.combined.unconsumed.cost[[1]][[j]])[which(names(summ.stats.by.strata.combined.unconsumed.cost[[1]][[j]]) %in% c("lower_bound (2.5th percentile)", "median", "upper_bound  (97.5th percentile)"))]<-
  #   c("combined_unconsumed_impact_lower_bound (2.5th percentile)", "combined_unconsumed_impact_median", "combined_unconsumed_impact_upper_bound  (97.5th percentile)")
  # names(summ.stats.by.strata.current.intake.cost[[1]][[j]])[which(names(summ.stats.by.strata.current.intake.cost[[1]][[j]]) %in% c("lower_bound (2.5th percentile)", "median", "upper_bound  (97.5th percentile)"))]<-
  #   c("current_intake_impact_lower_bound (2.5th percentile)", "current_intake_impact_median", "current_intake_impact_upper_bound  (97.5th percentile)")
  # names(summ.stats.by.strata.CF.intake.cost[[1]][[j]])[which(names(summ.stats.by.strata.CF.intake.cost[[1]][[j]]) %in% c("lower_bound (2.5th percentile)", "median", "upper_bound  (97.5th percentile)"))]<-
  #   c("CF_intake_impact_lower_bound (2.5th percentile)", "CF_intake_impact_median", "CF_intake_impact_upper_bound  (97.5th percentile)")
  # names(summ.stats.by.strata.current.intake.consumed.cost[[1]][[j]])[which(names(summ.stats.by.strata.current.intake.consumed.cost[[1]][[j]]) %in% c("lower_bound (2.5th percentile)", "median", "upper_bound  (97.5th percentile)"))]<-
  #   c("current_intake_consumed_impact_lower_bound (2.5th percentile)", "current_intake_consumed_impact_median", "current_intake_consumed_impact_upper_bound  (97.5th percentile)")
  # names(summ.stats.by.strata.CF.intake.consumed.cost[[1]][[j]])[which(names(summ.stats.by.strata.CF.intake.consumed.cost[[1]][[j]]) %in% c("lower_bound (2.5th percentile)", "median", "upper_bound  (97.5th percentile)"))]<-
  #   c("CF_intake_consumed_impact_lower_bound (2.5th percentile)", "CF_intake_consumed_impact_median", "CF_intake_consumed_impact_upper_bound  (97.5th percentile)")
  # names(summ.stats.by.strata.current.intake.unconsumed.cost[[1]][[j]])[which(names(summ.stats.by.strata.current.intake.unconsumed.cost[[1]][[j]]) %in% c("lower_bound (2.5th percentile)", "median", "upper_bound  (97.5th percentile)"))]<-
  #   c("current_intake_unconsumed_impact_lower_bound (2.5th percentile)", "current_intake_unconsumed_impact_median", "current_intake_unconsumed_impact_upper_bound  (97.5th percentile)")
  # names(summ.stats.by.strata.CF.intake.unconsumed.cost[[1]][[j]])[which(names(summ.stats.by.strata.CF.intake.unconsumed.cost[[1]][[j]]) %in% c("lower_bound (2.5th percentile)", "median", "upper_bound  (97.5th percentile)"))]<-
  #   c("CF_intake_unconsumed_impact_lower_bound (2.5th percentile)", "CF_intake_unconsumed_impact_median", "CF_intake_unconsumed_impact_upper_bound  (97.5th percentile)")
  # 
  # 
  ########################################
  # 
  # names(summ.stats.by.strata.cost[[3]][[j]])[which(names(summ.stats.by.strata.cost[[3]][[j]]) %in% c("lower_bound (2.5th percentile)", "median", "upper_bound  (97.5th percentile)"))]<-
  #   c("impact_lower_bound (2.5th percentile)", "impact_median", "impact_upper_bound  (97.5th percentile)")
  # names(summ.stats.by.strata.substitution.cost[[3]][[j]])[which(names(summ.stats.by.strata.substitution.cost[[3]][[j]]) %in% c("lower_bound (2.5th percentile)", "median", "upper_bound  (97.5th percentile)"))]<-
  #   c("substitution_impact_lower_bound (2.5th percentile)", "substitution_impact_median", "substitution_impact_upper_bound  (97.5th percentile)")
  # names(summ.stats.by.strata.combined.cost[[3]][[j]])[which(names(summ.stats.by.strata.combined.cost[[3]][[j]]) %in% c("lower_bound (2.5th percentile)", "median", "upper_bound  (97.5th percentile)"))]<-
  #   c("combinedimpact_lower_bound (2.5th percentile)", "combined_impact_median", "combined_impact_upper_bound  (97.5th percentile)")
  # names(summ.stats.by.strata.delta_forcost[[3]][[j]])[which(names(summ.stats.by.strata.delta_forcost[[3]][[j]]) %in% c("lower_bound (2.5th percentile)", "median", "upper_bound  (97.5th percentile)"))]<-
  #   c("delta_lower_bound (2.5th percentile)", "delta_median", "delta_upper_bound  (97.5th percentile)")
  # 
  # names(summ.stats.by.strata.combined.consumed.cost[[3]][[j]])[which(names(summ.stats.by.strata.combined.consumed.cost[[3]][[j]]) %in% c("lower_bound (2.5th percentile)", "median", "upper_bound  (97.5th percentile)"))]<-
  #   c("combined_consumed_impact_lower_bound (2.5th percentile)", "combined_consumed_impact_median", "combined_consumed_impact_upper_bound  (97.5th percentile)")
  # names(summ.stats.by.strata.combined.unconsumed.cost[[3]][[j]])[which(names(summ.stats.by.strata.combined.unconsumed.cost[[3]][[j]]) %in% c("lower_bound (2.5th percentile)", "median", "upper_bound  (97.5th percentile)"))]<-
  #   c("combined_unconsumed_impact_lower_bound (2.5th percentile)", "combined_unconsumed_impact_median", "combined_unconsumed_impact_upper_bound  (97.5th percentile)")
  # names(summ.stats.by.strata.current.intake.cost[[3]][[j]])[which(names(summ.stats.by.strata.current.intake.cost[[3]][[j]]) %in% c("lower_bound (2.5th percentile)", "median", "upper_bound  (97.5th percentile)"))]<-
  #   c("current_intake_impact_lower_bound (2.5th percentile)", "current_intake_impact_median", "current_intake_impact_upper_bound  (97.5th percentile)")
  # names(summ.stats.by.strata.CF.intake.cost[[3]][[j]])[which(names(summ.stats.by.strata.CF.intake.cost[[3]][[j]]) %in% c("lower_bound (2.5th percentile)", "median", "upper_bound  (97.5th percentile)"))]<-
  #   c("CF_intake_impact_lower_bound (2.5th percentile)", "CF_intake_impact_median", "CF_intake_impact_upper_bound  (97.5th percentile)")
  # names(summ.stats.by.strata.current.intake.consumed.cost[[3]][[j]])[which(names(summ.stats.by.strata.current.intake.consumed.cost[[3]][[j]]) %in% c("lower_bound (2.5th percentile)", "median", "upper_bound  (97.5th percentile)"))]<-
  #   c("current_intake_consumed_impact_lower_bound (2.5th percentile)", "current_intake_consumed_impact_median", "current_intake_consumed_impact_upper_bound  (97.5th percentile)")
  # names(summ.stats.by.strata.CF.intake.consumed.cost[[3]][[j]])[which(names(summ.stats.by.strata.CF.intake.consumed.cost[[3]][[j]]) %in% c("lower_bound (2.5th percentile)", "median", "upper_bound  (97.5th percentile)"))]<-
  #   c("CF_intake_consumed_impact_lower_bound (2.5th percentile)", "CF_intake_consumed_impact_median", "CF_intake_consumed_impact_upper_bound  (97.5th percentile)")
  # names(summ.stats.by.strata.current.intake.unconsumed.cost[[3]][[j]])[which(names(summ.stats.by.strata.current.intake.unconsumed.cost[[3]][[j]]) %in% c("lower_bound (2.5th percentile)", "median", "upper_bound  (97.5th percentile)"))]<-
  #   c("current_intake_unconsumed_impact_lower_bound (2.5th percentile)", "current_intake_unconsumed_impact_median", "current_intake_unconsumed_impact_upper_bound  (97.5th percentile)")
  # names(summ.stats.by.strata.CF.intake.unconsumed.cost[[3]][[j]])[which(names(summ.stats.by.strata.CF.intake.unconsumed.cost[[3]][[j]]) %in% c("lower_bound (2.5th percentile)", "median", "upper_bound  (97.5th percentile)"))]<-
  #   c("CF_intake_unconsumed_impact_lower_bound (2.5th percentile)", "CF_intake_unconsumed_impact_median", "CF_intake_unconsumed_impact_upper_bound  (97.5th percentile)")
  # ```
```

Still in loop: Then, for both lists, merge their contents into a data frame.
```{r merge_outcomes, eval=FALSE,echo=TRUE}
 list.names.intersect<-Reduce(intersect, lapply(outcome.data, colnames))
 
  all.summ.stats.by.strata<-Reduce(function(...) merge(..., by=list.names.intersect), outcome.data)
  all.summ.stats.by.strata.per.capita<-Reduce(function(...) merge(..., by=list.names.intersect), outcome.data.per.capita)
  # 
  # all.summ.stats.by.strata<-Reduce(function(...) merge(..., all = T),list(summ.stats.by.strata.delta_forcost[[1]][[j]],
  #                                                                         summ.stats.by.strata.cost[[1]][[j]], 
  #                                                                         summ.stats.by.strata.substitution.cost[[1]][[j]], 
  #                                                                         summ.stats.by.strata.combined.cost[[1]][[j]],
  #                                  
  #                                                                         summ.stats.by.strata.combined.consumed.cost[[1]][[j]],
  #                                                                         summ.stats.by.strata.combined.unconsumed.cost[[1]][[j]],
  #                                                                         summ.stats.by.strata.current.intake.cost[[1]][[j]],
  #                                                                         summ.stats.by.strata.CF.intake.cost[[1]][[j]],
  #                                                                         summ.stats.by.strata.current.intake.consumed.cost[[1]][[j]],
  #                                                                         summ.stats.by.strata.CF.intake.consumed.cost[[1]][[j]],
  #                                                                         summ.stats.by.strata.current.intake.unconsumed.cost[[1]][[j]],
  #                                                                         summ.stats.by.strata.CF.intake.unconsumed.cost[[1]][[j]]
  #                                                                         )
  #                                                                         )
  # 
  # all.summ.stats.by.strata.per.capita<-Reduce(function(...) merge(..., all = T),list(summ.stats.by.strata.delta_forcost[[3]][[j]],
  #                                                                                    summ.stats.by.strata.cost[[3]][[j]], 
  #                                                                                    summ.stats.by.strata.substitution.cost[[3]][[j]], 
  #                                                                                    summ.stats.by.strata.combined.cost[[3]][[j]],
  #                                                                                    
  #                                                                                    summ.stats.by.strata.combined.consumed.cost[[3]][[j]],
  #                                                                                    summ.stats.by.strata.combined.unconsumed.cost[[3]][[j]],
  #                                                                                    summ.stats.by.strata.current.intake.cost[[3]][[j]],
  #                                                                                    summ.stats.by.strata.CF.intake.cost[[3]][[j]],
  #                                                                                    summ.stats.by.strata.current.intake.consumed.cost[[3]][[j]],
  #                                                                                    summ.stats.by.strata.CF.intake.consumed.cost[[3]][[j]],
  #                                                                                    summ.stats.by.strata.current.intake.unconsumed.cost[[3]][[j]],
  #                                                                                    summ.stats.by.strata.CF.intake.unconsumed.cost[[3]][[j]]
  #                                                                                    )
  #                                                                                    )
  #                                  
```

Still in loop: Save the two outputs created (one for total and one for per capita) as csvs. Each of these data frames will have summary stats for all outputs of interest for subgroup j.
```{r save_merged_outcomes, eval=FALSE,echo=TRUE}
  setwd(paste(output_location, "/By_SubGroup", sep=""))
  #setwd("C:\\Users\\fcudhe01\\Box\\lasting_aim_3\\data\\out\\example_cost\\BySubGroup")
  write.csv(x=all.summ.stats.by.strata, file=paste("summary.output_by_", paste(strata.combos[[j]], collapse='_'), ".costenv.csv", sep=""))
  
  setwd(paste(output_location, "/per_capita/By_SubGroup", sep=""))
  #setwd("C:\\Users\\fcudhe01\\Box\\lasting_aim_3\\data\\out\\example_cost\\per_capita\\BySubGroup")
  write.csv(x=all.summ.stats.by.strata.per.capita, file=paste("summary.output.percapita_by_", paste(strata.combos[[j]], collapse='_'), ".costenv.csv", sep=""))
```
  
End loop.
```{r close_loop, eval=FALSE,echo=TRUE}
}
```
