---
title: "Complete PIF Analysis (Part 3)"
author: "Fred Cudhea & Brooke Bell"
date: "2025-05-19"
output: html_document
---

<style>
pre {
  overflow-x: auto;
}
pre code {
  word-wrap: normal;
  white-space: pre;
}
</style>


```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

```

This is documentation for "part 3" of the CRA code, which is for calculating the joint PIFs (attributable mort/incidence of multiple concurrent counterfactual exposures).

Define covar.vec.string (string vector of covariates of interest) so we read in the correct file (defining n.covar is obsolete).

```{r define_covar.vec.string, echo=FALSE}

covar.vec.string <- paste(covar.vec, sep="", collapse="")

n.covar <- length(covar.vec)

if(identical(covar.vec, c("Overall")))
  n.covar <- 0

```

Next, we'll define "calc.joint.PAFs", the function that is actually going to calculate the joint PIFs. It reads in a PIF simulations for a given dietary pattern, and calculates joint PIFs for the defined strata of interest.

```{r start_calc.joint.PAFs, echo=FALSE}

calc.joint.PAFs <- function(strata){
  
  # Read in PAF simulation file of interest. 
  # Note that the function itself only reads in strata, so output.location, diet_pattern, year.vec.string, 
  # and covar.vec.string need to be defined before calling the function.

  PAF.draws <- read.csv(file=paste(output_location, diet_pattern, "/all.PIFs_", year.vec.string, "_", covar.vec.string, "_", diet_pattern, ".csv", sep=""),
                      header=T)

  # If strata of interest includes one of the 4 ways of classifying disease (disease_type, disease_type1, disease_type2, disease_type3) 
  # then we get rid of the others from PAF.draws. These four are not mutually exclusive, they are different ways to the disease. 
  # Therefore, it doesn't make sense to stratify by more than one of these (Code won't work unless you take out the ones you don't use).

  # if contains disease type, then get rid of others
  if("disease_type" %in% strata){
    PAF.draws <- PAF.draws %>% select(-c("disease_type1", "disease_type2", "disease_type3"))
  } else if("disease_type1" %in% strata){
    PAF.draws <- PAF.draws %>% select(-c("disease_type", "disease_type2", "disease_type3"))
  } else if("disease_type2" %in% strata){
    PAF.draws <- PAF.draws %>% select(-c("disease_type", "disease_type1", "disease_type3"))
  } else if("disease_type3" %in% strata){
    PAF.draws <- PAF.draws %>% select(-c("disease_type", "disease_type1", "disease_type2"))
  } else{
    PAF.draws <- PAF.draws %>% select(-c("disease_type1", "disease_type2", "disease_type3"))
  }
  
  # Define number of sims (by counting up number of variables that start with "V")
  n.draws <- length(grep(pattern="V", x=names(PAF.draws)))
  
  PAF.draws$strata <- interaction(PAF.draws[,c(strata)])

  PAF.draws.by.strata.outcome <- split(x=PAF.draws, f=list(PAF.draws$strata))
  
  joint.PAFs.all.draws <- matrix(nrow=length(PAF.draws.by.strata.outcome), ncol=(length(strata)+n.draws)) # adding plus 1 for pathway
  joint.PAFs.all.draws <- as.data.frame(joint.PAFs.all.draws)
  names(joint.PAFs.all.draws)[1:(length(strata)+n.draws)] <- c(strata, paste("V", 1:n.draws, sep=""))  
  
  start <- which(names(PAF.draws.by.strata.outcome[[1]])=="V1")
  end <- start+n.draws-1
  
  for(i in 1:length(PAF.draws.by.strata.outcome)){
    joint.PAFs.all.draws[i,1:(length(strata))] <- PAF.draws.by.strata.outcome[[i]][1,strata]
    joint.PAFs.all.draws[i,length(strata)+c(1:n.draws)] <- 1-apply(1-PAF.draws.by.strata.outcome[[i]][,start:end], 
                                                                 MARGIN=2, FUN=prod)
    }
  return(joint.PAFs.all.draws)
}

# debug
joint.paf.draws=joint.PAFs.all.draws[[i]]
total.mort.draws=total.mort[[i]]

# caclulates joint mort, by multilpying joint paf with total mort
calc.joint.mort <- function(joint.paf.draws, total.mort.draws, strata){
  
  merged <- merge(joint.paf.draws, total.mort.draws)
  
  Joint.PAF.starting.point <- which(names(merged)=="V1")
  Joint.PAF.ending.point <- which(names(merged)==paste("V", nsim1, sep=""))
  totalmort.starting.point <- which(names(merged)=="X1")
  totalmort.ending.point <- which(names(merged)==paste("X", nsim1, sep=""))
  
  joint.mort <- cbind(merged[,c(strata)],
                      merged[,Joint.PAF.starting.point:Joint.PAF.ending.point]*merged[,totalmort.starting.point:totalmort.ending.point])
  return(joint.mort)
  
}

# create new combinations of strata without disease type overlap
strata0 <- c("age", "female", "race", "pathway", "disease_type")
strata1 <- c("age", "female", "race", "pathway", "disease_type1")
strata2 <- c("age", "female", "race", "pathway", "disease_type2")
strata3 <- c("age", "female", "race", "pathway", "disease_type3")
strata4 <- c("age", "female", "race", "outcome", "pathway")
strata5 <- c("age", "female", "race", "pathway")
strata_list <- list(strata0, strata1, strata2, strata3, strata5)

```

```{r}

# Once we know which dietary factors we will keep to calculate joint PIFs, we will subset PAF.draws to keep only
# those dietary factors

library(magrittr)

joint.PAFs.all.draws <- list()
total.mort <- list()
joint.mort.all.draws <- list()

for (i in 1:length(strata_list)) {
  
  strata <- strata_list[[i]]
  
  joint.PAFs.all.draws[[i]] <- calc.joint.PAFs(strata=strata)
  
  write.csv(x=joint.PAFs.all.draws[[i]], file=paste(output_location, diet_pattern, 
                                                    "/joint/joint_PIFs_all_draws_", paste(strata, collapse="_"), "_", year.vec.string, "_", diet_pattern, ".csv", sep=""))
  
  total.mort[[i]] <- read.csv(paste(output_location, diet_pattern, "/total_USmortality_draws_by_", 
                             strata %>% 
                               setdiff(., "pathway") %>%
                               paste(collapse = "_"),
                             "_", year.vec, "_", diet_pattern, ".csv", sep=""))
  
  joint.mort.all.draws[[i]] <- calc.joint.mort(joint.paf.draws=joint.PAFs.all.draws[[i]], total.mort.draws=total.mort[[i]], 
                                        strata=strata)
  
  write.csv(x=joint.mort.all.draws[[i]], file=paste(output_location, diet_pattern, "/joint/joint_mort_all_draws_", paste(strata, collapse="_"), "_", year.vec.string, "_", diet_pattern, ".csv", sep=""))

}

# calculate combos of interest
# need to create new strata.combos.of.interest.index for each disease type category

# first look at all strata combos
print(strata.combos)

# create new list of relevant strata combos
strata.combos.new <- strata.combos[strata.combos.of.interest.index]

print(strata.combos.new) #good

# strata.combos.new0 <- discard(strata.combos.new, function(x) "disease_type1" %in% x | "disease_type2" %in% x | "disease_type3" %in% x)
strata.combos.new0 <- keep(strata.combos.new, function(x) "disease_type" %in% x)
strata.combos.new1 <- keep(strata.combos.new, function(x) "disease_type1" %in% x)
strata.combos.new2 <- keep(strata.combos.new, function(x) "disease_type2" %in% x)
strata.combos.new3 <- keep(strata.combos.new, function(x) "disease_type3" %in% x)
strata.combos.new4 <- keep(strata.combos.new, function(x) "outcome" %in% x)
strata.combos.new5 <- discard(strata.combos.new, function(x) "disease_type" %in% x | "disease_type1" %in% x | "disease_type2" %in% x | "disease_type3" %in% x | "outcome" %in% x)

# new function
calculate_combos <- function(my.strata.combos, x){

  for(i in 1:length(my.strata.combos)){
    
    print(i)
    print(my.strata.combos[[i]])
    print("")
    
    sum.stats.byX.joint.attr.mort <- Sum.by.strata.joint(allmort=joint.mort.all.draws[[x]], totalmort=totalmort, pop=pop.draws, covar=my.strata.combos[[i]])
    
    write.csv(x=sum.stats.byX.joint.attr.mort[[1]], 
              file=paste(output_location, diet_pattern, "/joint/summarystats_joint_attributable_USmortality_", "by_", 
                         paste(my.strata.combos[[i]], sep="", collapse="_"), "_", year.vec.string, "_", diet_pattern, "_new.csv", sep=""), 
              row.names=FALSE)
    
    write.csv(x=sum.stats.byX.joint.attr.mort[[2]], 
              file=paste(output_location, diet_pattern, "/joint/joint_attributable_USmortality_draws_", "by_", 
                         paste(my.strata.combos[[i]], sep="", collapse="_"), "_", year.vec.string, "_", diet_pattern, ".csv", sep=""), 
              row.names=FALSE)
    
    write.csv(x=sum.stats.byX.joint.attr.mort[[3]], 
              file=paste(output_location, diet_pattern, "/joint/RE_joint_PIFs_draws_", "by_", 
                         paste(my.strata.combos[[i]], sep="", collapse="_"), "_", year.vec.string, "_", diet_pattern, ".csv", sep=""), 
              row.names=FALSE)
    
    write.csv(x=sum.stats.byX.attr.mort[[4]], 
              file=paste(output_location, diet_pattern, "/joint/RE_joint_PIFs_draws_", "by_", 
                         paste(my.strata.combos[[i]], sep="", collapse="_"), "_", year.vec.string, "_", diet_pattern, ".csv", sep=""), 
              row.names=FALSE)
    
  }
  
}

# apply
calculate_combos(my.strata.combos = strata.combos.new0, x=1)
calculate_combos(my.strata.combos = strata.combos.new1, x=2)
calculate_combos(my.strata.combos = strata.combos.new2, x=3)
calculate_combos(my.strata.combos = strata.combos.new3, x=4)
calculate_combos(my.strata.combos = strata.combos.new4, x=5)
calculate_combos(my.strata.combos = strata.combos.new5, x=6)
  
```

